Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-12 prop_letter.tex
conclusion

>>>>

Foundational concepts in quantum mechanics, such as Gleason and
Kochen-Specker theorems, rely in a very subtle way on the use of
unbounded resources. By assuming infinitely precise measurements,
these two insightful theorems underline two fundamental aspects of
quantum mechanics. On the one hand, Gleason's result establishes a
relationship between quantum states and probabilities uniquely defined
by Born's rule, on the other, Kochen-Specker unveils a distinctive
aspect of physical reality, the fact that it is contextual.  Our goal
in this paper has been to analyze the physical consequences of a
mathematical framework that allows for finite precision measurements
by introducing the concept of quantum interval-valued probability. The
latter incorporates uncertainty in the measurement results by defining
fuzzy probability measures, and includes standard quantum measurement
as the particular instance of sharp, infinitely precise, intervals.
In addition, we showed how these two theorems emerge as limiting cases
of this very same framework, thus connecting two seemingly unrelated
aspects of quantum physics. Most importantly, we concluded that
arbitrary finite precision measurement conditions nullify the main
tenets of both theorems.
